%-------------------------
% ONE-PAGE ATS Resume | Jagjeet Singh | SDE-1
% Overleaf / pdfLaTeX
%-------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

% Commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}
  \end{tabular*}\vspace{-6pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%===========================================
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jagjeet Singh} \\ \vspace{3pt}
    \small
    \faPhone\ \href{tel:+917814239065}{+91-78142-39065} \;$|$\;
    \faEnvelope\ \href{mailto:workforjagjeet@gmail.com}{workforjagjeet@gmail.com} \;$|$\;
    \faLinkedin\ \href{https://linkedin.com/in/jagjeetsingh}{linkedin.com/in/jagjeetsingh} \;$|$\;
    \faGithub\ \href{https://github.com/jagjeetsingh78}{github.com/jagjeetsingh78} \;$|$\;
    \faCode\ \href{https://leetcode.com/}{leetcode.com/jagjeet}
\end{center}

\vspace{-8pt}

%-----------SUMMARY-----------
\section{Summary}
\small{B.Tech (ECE) student with \textbf{1+ year of internship experience} in mobile, web, and backend engineering. Solved \textbf{170+ LeetCode problems} (DSA in Java). Quick learner across stacks -- Flutter, React, Node.js, FastAPI. Seeking SDE-1 at a product-driven MNC.}

\vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Nanak Dev University, Amritsar}{Punjab, India}
      {B.Tech -- Electronics and Communication Engineering $|$ \textbf{CGPA: 7.53}}{Aug 2023 -- May 2027}
  \resumeSubHeadingListEnd

\vspace{-4pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AGOMUC Program}{Delhi, India}
      {Software Engineer Intern}{Dec 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built production cross-platform apps in \textbf{Flutter} from Figma designs using \textbf{BLoC} architecture.}
        \resumeItem{Developed \textbf{RESTful APIs} with \textbf{FastAPI + MongoDB}; deployed serverless functions via \textbf{Firebase Cloud Functions}.}
        \resumeItem{Integrated \textbf{Firebase Cloud Messaging (FCM)} for real-time push notifications across the mobile app.}
      \resumeItemListEnd

    \resumeSubheading
      {Jasminder Web Services Point}{Kotkapura, Punjab}
      {Flutter Developer Intern}{June 2025 -- Nov 2025}
      \resumeItemListStart
        \resumeItem{Delivered Flutter apps with \textbf{Firebase \& Supabase} integration using \textbf{GetX / Provider} state management.}
        \resumeItem{Built admin dashboards with FlutterFlow; integrated third-party \textbf{REST APIs} and handled async data flows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\vspace{-4pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{Get Well Go} -- Doctor Booking App $|$ \emph{Flutter, Node.js, Express.js, MongoDB, REST API}}{June -- July 2025}
        \resumeItemListStart
          \resumeItem{Full-stack app for doctor search and appointment booking with real-time slot availability.}
          \resumeItem{Built JWT-authenticated REST APIs with Node.js/Express; modeled MongoDB schemas for bookings and users.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{MERN Stack Web App} $|$ \emph{React.js, Node.js, Express.js, MongoDB}}{2025}
        \resumeItemListStart
          \resumeItem{End-to-end MERN application with JWT auth, protected routing, and MongoDB Atlas cloud persistence.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\vspace{-4pt}

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages:} Java, Dart, JavaScript, Python, C++, HTML5, CSS3 \\[2pt]
    \textbf{Mobile:} Flutter (BLoC, GetX, Provider, Riverpod), FlutterFlow, Android/Kotlin \textit{(learning)} \\[2pt]
    \textbf{Web \& Backend:} React.js, Angular \textit{(learning)}, Node.js, Express.js, FastAPI, REST API Design \\[2pt]
    \textbf{Databases \& Cloud:} MongoDB, Firebase, Supabase (PostgreSQL), MySQL, Firebase Cloud Functions \\[2pt]
    \textbf{DSA:} \textbf{170+ LeetCode problems} -- Arrays, Trees, Graphs, DP, Recursion, Linked Lists \textit{(Java)} \\[2pt]
    \textbf{Tools:} Git, GitHub, Postman, VS Code, Android Studio, Agile/Scrum
    }}
 \end{itemize}

\vspace{-4pt}

%-----------LEADERSHIP-----------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Electronics Student Forum -- Web \& Design Team}{GNDU, Amritsar}
      {Member}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Managed department web presence and digital assets; co-organized technical events for 200+ students.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
